---
title: "Fabric canvas<br>.gray[for xaringan]"
pagetitle: "🎨 Fabric canvas for xaringan"
subtitle: "🎨"
author: "<a href='https://pkg.garrickadenbuie.com/xaringanExtra'>xaringanExtra<a>"
date: 'Add .purple[fabric canvases] to mark up your xaringan slides '
output:
  xaringan::moon_reader:
    css: [robot-fonts, robot]
    lib_dir: libs
    nature:
      highlightStyle: 'atom-one-light'
---

```{r xaringanExtra-canvas, echo=FALSE}
options(htmltools.dir.version = FALSE)
```

```{css, echo=FALSE}
.gray { color: #999; }
.big { font-size: 200%; }
.purple { color: #A53B87; }
.green { color: #42B983; }
```

## Draw on me!

- This feature builds on top of the amazing `fabric.js` library to support `xaringan`/`remark` slides

- To use this feature, all you need to do is add one line of code to your `xaringan` Rmd file

```{r}
xaringanExtra::use_fabric()
```

- The `xaringanExtra::use_fabric()` function can accept arguments to configure the `pen_color`, `pen_size`, `eraser_color`, and `eraser_size`. See `?use_fabric` for more details.

- Start by clicking the "edit" icon in the top-right corner toolbox, then click and drag to add mark up! Click the eraser button to erase lines, or the trash can to clear the entire canvas!

- This feature even has full-support for touch devices too!

---

## Even works with widgets

```{r echo=FALSE, out.height='70%', out.width='100%', results='asis'}
library(leaflet)
m <- leaflet() %>% addTiles()
m <- m %>% setView(-93.65, 42.0285, zoom = 17)
m
```

---

## And plots...

```{r}
plot(mtcars$mpg, mtcars$hp)
```
