To add **clipboard** to your xaringan presentation or R Markdown document,
add the following code chunk to your slides' R Markdown file.

````markdown
```{r xaringanExtra-clipboard, echo=FALSE}`r ''`
xaringanExtra::use_clipboard()
```
````

You can also customize the text that is shown
by default when hovering over a code chunk
with the `button_text` argument.
Use `success_text` to specify the text shown when the copy action works,
or `error_text` for the text shown when the copy action fails.
If the copy action fails, the text will still be selected, 
so the user can still manually press `Ctrl+C` to copy the code chunk.

These options accept raw HTML strings,
so you can achieve an icon-only appearance using FontAwesome icons:

````markdown
```{r xaringanExtra-clipboard, echo=FALSE}`r ''`
htmltools::tagList(
  xaringanExtra::use_clipboard(
    button_text = "<i class=\"fa fa-clipboard\"></i>",
    success_text = "<i class=\"fa fa-check\" style=\"color: #90BE6D\"></i>",
    error_text = "<i class=\"fa fa-times-circle\" style=\"color: #F94144\"></i>"
  ),
  rmarkdown::html_dependency_font_awesome()
)
```
````
