```{r echo=FALSE, results="asis"}
if (!exists("INCLUDE_CHILD_HEADER") || isTRUE(INCLUDE_CHILD_HEADER)) {
	cat("# Style Panelset")
}
```

To customize the appearance of your panels,
you can use `style_panelset_tabs()` 
called directly in an R chunk in your slides.

````markdown
```{r echo=FALSE}`r ''`
style_panelset_tabs(foreground = "honeydew", background = "seagreen")
```
````

The panelset uses opacity to soften the in-active tabs
to increase the chances that the tabs will work with your slide theme.
If you decide to change your tab colors
or to use solid colored tabs,
you'll likely want to set `inactive_opacity = 1` in `style_panelset()`
(or the corresponding `--panel-tab-inactive-opacity` CSS variable).

Behind the scenes, 
`style_panelset_tabs()` updates the values of
[custom CSS properties](https://developer.mozilla.org/en-US/docs/Web/CSS/--*)
that define the panelset appearance.
If you'd rather work with CSS,
the default values of these properties are shown in the CSS code below.
You can copy the whole CSS block to your slides 
and modify the values to customize the style to fit your presentation.

````markdown
```{css echo=FALSE}`r ''`
.panelset {
   --panel-tab-foreground: currentColor;
   --panel-tab-background: unset;
   --panel-tab-active-foreground: currentColor;
   --panel-tab-active-background: unset;
   --panel-tab-active-border-color: currentColor;
   --panel-tab-hover-foreground: currentColor;
   --panel-tab-hover-background: unset;
   --panel-tab-hover-border-color: currentColor;
   --panel-tab-inactive-opacity: 0.5;
   --panel-tabs-border-bottom: #ddd;
   --panel-tab-font-family: Menlo, Consolas, Monaco, Liberation Mono, Lucida Console, monospace;
}
```
````
