```{r echo=FALSE, results="asis"}
if (!exists("INCLUDE_CHILD_HEADER") || isTRUE(INCLUDE_CHILD_HEADER)) {
  cat("# Panelset knitr Chunks")
}
```

A common use-case for **panelset**
is to show the code and its output in separate tabs.
For example,
you might want to first show the code to create a plot in the first tab,
with the plot itself in a second tab.
On slides where space is constrained,
this approach can be useful.

To help facilitate this process,
**panelset** provides a `panelset` chunk option.
When set to `TRUE`,
the code is included in a panel tab named _Code_
and the output is included in a panel tab named _Output_.
Note that you still need to wrap this chunk in a panelset-creating container.

````markdown
.panelset[
```{r panelset = TRUE}`r ''`
list(
  normal = rnorm(10),
  uniform = runif(10),
  cauchy = rcauchy(10)
)
```
]
````

You can also set the `panelset` chunk option to a named vector,
where the `source` item is the tab name for the source code
and the `output` item is the tab name for the code output.

````markdown
```{r panelset = c(source = "ggplot2", output = "Plot")}`r ''`
ggplot(Orange) +
  aes(x = age, y = circumference, colour = Tree) +
  geom_point() +
  geom_line() +
  guides(colour = FALSE) +
  theme_bw()
```
````

When your code contains multiple expressions and outputs,
you may also want to set the `results = "hold"` chunk option.
Currently, knitr uses `results = "markup"` as the default,
in which case each code expression and output pair will generate a pair of tabs.

````markdown
```{r panelset = TRUE, results="hold"}`r ''`
print("Oak is strong and also gives shade.")
print("The lake sparkled in the red hot sun.")
```
````

Finally, panelset chunks also work in R Markdown documents,
but they must be encapsulated in `<div class="panelset">` and `</div>`

````markdown
<div class="panelset">

```{r panelset = TRUE}`r ''`
print("Oak is strong and also gives shade.")
```

</div>
````

or appear inside a section with the panelset class.

````markdown
### A Random Sentence {.panelset}

```{r panelset = TRUE}`r ''`
print("Oak is strong and also gives shade.")
```

````
